Extending the WebID Protocol with Access Delegation

### 2012-08-03 paper.tex

\subsection{MyProfile description}
MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet. Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.

>>>>

\subsection{MyProfile description}
MyProfile\footnote{http://myprofile-project.org/} intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet. Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.
